Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2021-07-18 ms/Thesis/thesis.tex
add first page

@@

\begin{document}
\maketitle

\pagebreak
{\large This work was carried out under the supervision of \textbf{Dr. Yoav Ram} from the School of Zoology, Faculty of Life Sciences, Tel Aviv University.}
\pagebreak

@@

In this work, we have studied a cultural evolution model in which interactions are modeled as a Prisoner's Dilemma game.
We also assumed that in each generation individuals have only one meaningful interaction.
It would be interesting to investigate a model in which multiple games are played in each generation. 
This would make the model more realistic and more complicated to solve. To overcome the math complication, numerical simulations can be used. 
The model can be further expanded by changing the game to Stag Hunt game. \citet{tomasello2012two} claim that Stag Hunt game can better explain evolution of cooperation in humans,
because humans often collobrate in Stag Hunt type situations in which all participants had alternatives but anticipated an even greater benefit from
successful capturing of the stag \citep{mitani2012evolution}. Therefore, changing the model so each interaction would be model as Stag Hunt game could help us better understand cooperartion in humans.

In our model we assumed that the model parameters such as vertical transmission($v$), horizontal transmission ($T_A \,, T_B$), benfit from cooperartion ($b$), cost of cooperartion ($c$) and interaction-transmission association ($\alpha$) do not change over time.
However, in reality things are changing. For example, during different time of the year, behavior can be changed due to weather \citep{azcarate2007microclimatic}, predator abundance \citep{briffa2008comparing} and food abundance \citep{johnson2001foraging}.
This could lead to changes in the model parameters.
Further investigation is needed to learn about the effect of such changes in behavior.

>>>>

\usepackage{datetime}
\newdateformat{monthyeardate}{%
  \monthname[\THEMONTH], \THEYEAR}

@@

\begin{document}
\begin{titlepage}
	\centering
	\includegraphics[width=0.4\textwidth]{IDC_logo}\par\vspace{1cm}
	{\huge Interdisciplinary Center Herzliya \par}
	{\Large Efi Arazi School of Computer Science \par}
	{\Large M.Sc. Program - Research Track \par}

	\vspace{1.5cm}
	{\Huge Non-Vertical Cultural 
  Transmission, 
  Assortment, and the 
  Evolution of 
  Cooperation \par}
	\vspace{1.5cm}
	{\large by\par}
	{\Large\bfseries Dor Cohen\par}
	\vspace{1cm}
	{\large Supervised by Dr. Yoav Ram\par}
	{School of Zoology, Faculty of Life Sciences, Tel Aviv University\par}

	\vspace{1cm}
	{M.Sc. dissertation, submitted in partial fulfillment of the requirements\par}
	{for the M.Sc. degree, research track, School of Computer Science\par}
	{Interdisciplinary Center Herzliya}

	\vspace{1cm}
	% Bottom of the page
	{\large \monthyeardate\today \par}

\end{titlepage}

@@

In this work, we have studied a cultural evolution model in which interactions are modeled as a Prisoner's Dilemma game.
We also assumed that in each generation individuals have only one meaningful interaction.
It would be interesting to investigate a model in which multiple games are played in each generation. 
This would make the model more realistic and more complicated to solve. To overcome the math complication, numerical simulations can be used. 
The model can be further expanded by changing the game to Stag Hunt game. \citet{tomasello2012two} claim that Stag Hunt game can better explain evolution of cooperation in humans,
because humans often collobrate in Stag Hunt type situations in which all participants had alternatives but anticipated an even greater benefit from
successful capturing of the stag \citep{mitani2012evolution}. Therefore, changing the model so each interaction would be model as Stag Hunt game could help us better understand cooperartion in humans.
e
In our model we assumed that the model parameters such as vertical transmission($v$), horizontal transmission ($T_A \,, T_B$), benfit from cooperartion ($b$), cost of cooperartion ($c$) and interaction-transmission association ($\alpha$) do not change over time.
However, in reality things are changing. For example, during different time of the year, behavior can be changed due to weather \citep{azcarate2007microclimatic}, predator abundance \citep{briffa2008comparing} and food abundance \citep{johnson2001foraging}.
This could lead to changes in the model parameters.
Further investigation is needed to learn about the effect of such changes in behavior.
